Browsernative Microservices

### 2017-01-25 paper.tex
pdf/tex build

In the last four years the average transfer size of a webpage doubled to
currently around 2.5 MB.{[}\^{}http {]}Subtracting images, fonts or
other content the size of HTML, CSS and JS sums up to a total average of
550 kb. One character weights around 1 byte which means an average
webpage is delivering 550.000 character or around 125 pages of
single-spaced text. Frederic Filloux calculated the ratio of real
content on different newspaper websites and came to the conclusion, that
only round about 5-6 \% of the transferred characters made for
consumption.{[}1{]}

>>>>

In the last four years the average transfer size of a webpage doubled to
currently around 2.5 MB.\footnote{\href{http://httparchive.org/trends.php}{HTTPArchive
  Trends}} Subtracting images, fonts or other content the size of HTML,
CSS and JS sums up to a total average of 550 kb. One character weights
around 1 byte which means an average webpage is delivering 550.000
character or around 125 pages of single-spaced text. Frederic Filloux
calculated the ratio of real content on different newspaper websites and
came to the conclusion, that only round about 5-6 \% of the transferred
characters made for consumption.{[}1{]}
